 

### 2021-07-12 vertical-thermal-review.Rmd
fix up Tleaf alternate versions
#48

**Nidhi's rearrangement:**

~~Solar and longwave radiation can dramatically elevate $T_{leaf}$ well above $T_{air}$ (Fig. `r fig_leaf_T`a) because the heat absorbed through high irradiance can be greater than heat lost through sensible heat (via $g_a$; *i.e.*, boundary layer conductance) and $\lambda E$ (via $g_s$ *ie.* stomatal conductance and $E$ ie evaporation)[@bonan_ecological_2016].

@@

NEON sites (in Fig. `r fig_NEON_vertical`) might not exactly reflect the $T_{leaf}$ pattern we might expect, partly because $T_{bio}$ measured using infrared sensor, reflects a wide swath of biological temperatures. But, recent advances in $T_{leaf}$ modelling that we outline [see Scaling across Space and Time], will enhance our understanding of large scale $T_{leaf}$ vertical patterns [@stillImagingCanopyTemperature2021].~~

**Krista's version:**

>>>>

**version 1 (for rest of biophyscial drivers subsection-- coauthors, please let us know which is better):**

Solar and longwave radiation can dramatically elevate $T_{leaf}$ well above $T_{air}$ (Fig. `r fig_leaf_T`a) because the heat absorbed through high irradiance can be greater than heat lost through sensible heat (via $g_a$; *i.e.*, boundary layer conductance) and $\lambda E$ (via $g_s$ *ie.* stomatal conductance and $E$ ie evaporation)[@bonan_ecological_2016].

@@

**version 2 (for rest of biophyscial drivers subsection-- coauthors, please let us know which is better):**
